Long name of the paper

### 2018-10-01 anzjs2018/sections/03_models.tex
network model

Two parts to this - first, the prior prediction step; then, the data update step.

>>>>

The second part of this appraoch involves a network model of transit network travel times along links in the network.
Reliable ETAs will require a historical data component,
used as a prior in the absense of data as well as for
predicting future states, 
and a realtime update component where the travel times of vehicles
are used to update the current estimate of network state.

The model will be another recursive Bayesian model as used for the vehicle state,
as this provides a simple way to model realtime data.
Since travel times can safely be assumed to be unimodal,
we use an information filter (IF),
which is a transformation of the Kalman filter
using information instead of covariance,
and allows the simple combination of multiple observations,
for example when multiple buses traverse a road in the same update.
The prediction step will involve a transition function that incorporates historical data
and the update step will weight between observed and predicted travel times.

The network state $\Theta_c = \{\theta_c^j\}_{j = 1}^J$ is the travel time 
of transit vehicles along road segment $j$ at time $t_c$.
In this implementation, we are assuming independence between each segment
to provide a simple basis for the model; of course in reality this
is not true and future work will investigate ways of incorporating this.

Using an IF requires a transition matrix, $\mathbf{F}_c$;
however, in this case the travel time model is constant so no
transition matrix is required (i.e., $\mathbf{F}_c = 1$).
Let $\Delta_c = t_c - t_{c-1}$ and $P_c^j$ the state uncertainty
with system noise $Q_c = \Delta_c \sigma_b^2$, then the update equations are
simply the normal KF update equations,
\begin{align}
\label{eq:kf_transition}
\hat\theta^j_{c|c-1} &= \hat\theta^j_{c|c-1} \\
P^j_{c|c-1} &= P^j_{c-1|c-1} + Q_c
\end{align}

For the update step, however, we need to transform into an information
space parameterised by the information matrix 
$\mathbf{Z}^j_{c|c-1} = P_{c|c-1}^{-1}$ 
and the information vector $\mathbf{\hat z}^j_{c|c-1} = \hat\theta_{c|c-1} P_{c|c-1}^{-1}$.
The measurement data obtained from the vehicle model are
the travel time of vehicle $m$ along segment $j$,
$\bar b^m_j$, and the uncertainty $s^m_j$.
These can be transformed to a measurement information covaraince matrix
and vector using the measurement matrix $\mathbf{H} = 1$ since,
in this case, the observed state is the underlying state we are estimating (travel time).
\begin{equation}
I^m_{jc} = \frac{1}{(s^m_j)^{2}}\quad\text{and}\quad
i^m_{jc} = \frac{\bar b^m_j}{(s^m_j)^2}
\end{equation}
The information update is now the sum of the information for all vehicles
that traversed the segment since the last update, so
\begin{align*}
\mathbf{Z}^j_{c|c} &= \mathbf{Z}^j_{c|c-1} + \sum_{m=1}^M I^m_{jc} \\
\mathbf{\hat i}^j_{c|c} &= \mathbf{\hat z}^j_{c|c-1} + \sum_{m=1}^M i^m_{jc}
\end{align*}
which are easily transformed back to get the desired state parameters.
\begin{equation}
\hat\theta^j_{c|c} = \frac{\mathbf{\hat z}^j_{c|c}}{\mathbf{Z}^j_{c|c}} 
\quad\text{and}\quad
P^j_{c|c} = \frac{1}{\mathbf{Z}^j_{c|c}}
\end{equation}
